Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
intro fix

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq amount to more than 160,000 lines of code and 11,000 lemmas~\cite{Nie2020a}, while Lean's Mathlib consists of more than 140,000 lines of code and 34,000 declarations~\cite{Mathlib}. However, after a key mathematical definition or result is added to a library, it needs be \emph{documented}~\cite{alectryonpaper} and \emph{maintained}~\cite{vanDoorn2020}.

>>>>

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq amount to more than 160,000 lines of code and 11,000 lemmas~\cite{Nie2020a}, while Lean's Mathlib consists of more than 140,000 lines of code and 34,000 declarations~\cite{Mathlib}. However, after a key mathematical definition or result is added to a library, it must be \emph{documented and maintained}~\cite{vanDoorn2020,alectryonpaper}.
